
\begin{abstract}
Routing policies for heterogeneous parallel queues face a fundamental tension between state-awareness and capacity-awareness. While classical policies typically prioritize only one, and standard reinforcement learning (RL) policy-gradient approaches without guided initialization typically lack formal stability, we propose GibbsQ---a framework that bridges this gap via entropy-regularized routing.

At the \textbf{analytical level}, we formally prove positive Harris recurrence for three routing laws: raw softmax, UAS (under the strict load condition $\totcap > \arrate$), and a stability-certified calibrated subclass (SCUAS) under an explicit parameter-conditional drift bound. These proofs yield computable drift constants; notably, the UAS constants are temperature-independent.

At the \textbf{empirical level}, we introduce Calibrated UAS, a closed-form extension of UAS with three tunable parameters. We find that while Calibrated UAS delivers superior performance---reducing steady-state queue lengths by 8.84\% and 12.6\% relative to JSSQ and baseline UAS respectively---the benchmark-default setting is not theorem-certified. A post-validation audit confirms that the audited benchmark configuration yields negative sufficient drift constants, thus these results remain empirical rather than certified in this study. However, we identify a benchmark-specific piecewise Lyapunov candidate that materially narrows the case for future certification.

Finally, we quantify the \textbf{teacher-choice effect} in the learned-policy layer. We demonstrate that the default neural policy (trained from the analytical UAS teacher) actually underperforms the JSSQ and UAS heuristics. However, under a controlled extended-horizon ablation protocol (Protocol B, rather than the primary anchor benchmark), the neural variant initialized from Calibrated UAS, fine-tuned via \reinforce{}, and selected via a best-of-5 ensemble using a separate held-out validation set to mitigate selection bias, achieves the lowest point estimate of queue length among all evaluated policies under this protocol, outperforming even its closed-form teacher. This performance gain is strictly directional and does not achieve statistical significance, functioning primarily to identify behavioral potential and motivate advanced variance reduction techniques. However, the directional advantage persists across 16 operating configurations and into near-critical regimes up to $\rho = 0.98$ (attaining an 8.85\% directional improvement with uncertainty underestimated at near-critical loads; see Table~\ref{tab:critical}). Note that our formal stability proofs and empirical evaluations assume standard M/M/1 dynamics; robustness against model misspecifications (e.g., non-exponential service) remains outside the current scope.
\end{abstract}
