
\section{N-GibbsQ: Learned Neural Policy}
\label{sec:neural_policy}

The $\ngibbsq$ policy is a neural routing law that maps queue states to routing distributions.
It serves as an \emph{empirical} approximation and is not part of the formal stability theorems.

\subsection{Architecture}

The network takes as input the queue-length vector $\Qstate \in \Nats^\Nservers$ and service rates $\srvrate \in \Reals_+^\Nservers$.
Queue lengths are preprocessed via $\log(1 + \Qlen{i})$ to compress the dynamic range.
A feedforward network with two hidden layers (widths 32 and 16, respectively) and ReLU activations produces logits, passed through a softmax to yield
\begin{equation}
\label{eq:neural_output}
\rprob{i}(\Qstate, \srvrate; \theta) = \softmax\!\bigl(f_\theta(\Qstate, \srvrate)\bigr)_i,
\end{equation}
a valid probability distribution on $\Simplex$ by construction.

\subsection{Two-Phase Training Pipeline}

\paragraph{Phase~1: Behavior Cloning}
The network is trained via cross-entropy loss against an analytical teacher policy (UAS with $\temp = 10$ by default; the ablation in \cref{sec:exp:ablation} also evaluates Calibrated UAS).
Training runs for 1{,}000 steps, minimizing cross-entropy to faithfully capture the full routing distribution structure across the simplex. At convergence, this objective provides a stable initialization for Phase~2, yielding an exact top-1 action matching accuracy of 99.2\% (best seed, with an inter-seed range of 97--99\%) and a terminal KL divergence of $1.16 \times 10^{-3}$ across sampled validation state points, ensuring high-fidelity empirical correlation in the distribution tails.

\paragraph{Phase~2: REINFORCE Fine-Tuning}
Starting from BC-pretrained weights, policy gradient optimization proceeds via \reinforce{} with a running-average baseline~\cite{williams1992simple}, using 16-episode batches over 15 epochs (each episode simulates 1{,}000 time units).
We intentionally employ vanilla \reinforce{} rather than modern alternatives such as PPO (with its surrogate clipped objective) or SAC (a maximum-entropy off-policy architecture). This deliberate experimental design strictly isolates the impact of the starting distribution, demonstrating that guided initialization via behavior cloning---rather than advanced trust-region mechanics---is what fundamentally resolves routing instability. This deliberate constraint means any residual gap between the neural and closed-form policies is attributable to optimization noise rather than architectural capacity---a conservative choice that strengthens rather than weakens the directional finding.
The gradient estimator achieves perfect directional agreement with the true gradient (cosine similarity $1.0$; \cref{sec:appendix_gradient}).
Full hyperparameters are given in \cref{sec:appendix_training}.
Empirical results for $\ngibbsq$ are reported in \cref{sec:experiments}.
