
\section{Discussion, Limitations, and Future Directions}
\label{sec:discussion}

\subsection{The Teacher-Choice Effect}

The ablation study showcases a clear rank ordering (where $\succ$ denotes strictly lower mean total queue length): Calibrated UAS teacher ($9.82$) $\succ$ UAS teacher ($11.14$) $\succ$ scratch ($5{,}451$; diverged).
The $1.32$-unit gap between the Calibrated UAS teacher and the UAS teacher exceeds the impact of all architectural modifications evaluated (log-normalization, zero-init), which identifies teacher quality as a primary design factor in this empirical setting.

This observation has a natural interpretation.
Essentially, behavior cloning positions the neural policy's parameters in a region from which \reinforce{} fine-tuning makes local improvements.
A competent teacher provides a better initialization, from which \reinforce{} then attempts to drive further improvement, whereas a weaker initialization forces fine-tuning to expend its efforts on overcoming the deficit.
The developed policy in this study can be characterized as local fine-tuning within the initialization region, rather than global policy search.
The offline BC phase does not address the distributional shift~\cite{ross2011reduction}.
On-policy data collection during pretraining could further improve initialization quality.

\subsection{Why Calibrated UAS Outperforms UAS}

Calibrated UAS alters three key components of UAS, each influencing performance in a specific way:
\begin{itemize}
\item \textbf{Tempered normalization} ($\calbeta = 0.85$): the denominator $\srvrate_i^{\calbeta}$ increases more slowly than $\srvrate_i$, reducing the routing-mass differential between fast and slow servers.
\item \textbf{Softened prior} ($\calgamma = 0.5$): the pre-exponential factor $\srvrate_i^{\calgamma}$ reduces the routing bias toward fast servers relative to UAS's proportional-to-$\srvrate_i$ prior.
\item \textbf{Reduced look-ahead} ($\caloffset = 0.5$): the energy function's additive constant is decreased from $1$ (UAS: $\Qlen{i}+1$) to $0.5$, shifting routing slightly toward current-state responsiveness.
\end{itemize}

We conjecture that these adjustments improve steady-state performance by rebalancing load distribution, the tempered normalization and softened prior jointly reduce over-routing to fast servers, while the diminished offset increases responsiveness to current state.
This conjecture is consistent with the Gini coefficients in Table~\ref{tab:policy}: Calibrated UAS achieves $G = 0.174$ versus UAS's $G = 0.328$, a 47\% reduction in load imbalance, suggesting that the tempered parameters substantially balance routing mass across servers.
The $1.45$-unit improvement over UAS ($10.04$ vs.\ $11.495$) confirms substantial empirical gain beyond the provably stable parameterization.

\subsection{Limitations}

\begin{enumerate}[label=\textbf{L\arabic*.}, leftmargin=2.2em]
\item \textbf{Full Calibrated UAS family remains open:}
Section~\ref{sec:calibrated_uas} identifies the stability-certified subclass SCUAS under the explicit sufficient condition $\varepsilon_{\calbeta,\calgamma,\caloffset}>0$.
However, our audit in Table~\ref{tab:scuas_audit} finds that the benchmark default point $(\calbeta, \calgamma, \caloffset) = (0.85, 0.5, 0.5)$ yields $\varepsilon_{\calbeta,\calgamma,\caloffset} < 0$ under the anchor configuration.
While we provide \textbf{numerical evidence} for negative drift through a JAX-based verification loop (reported in Table~\ref{tab:piecewise_candidate}), a formal symbolic proof for the unrestricted family remains an open theoretical question. This establishes a definitive split in our results: the benchmark-default policy is a competitive empirical baseline, but it is not yet theorem-certified.

\item \textbf{Default learned configuration is not the strongest:}
The standard $\ngibbsq$ model (trained with a UAS teacher) achieves $11.68$ in the anchor benchmark, underperforming JSSQ ($11.02$) and Calibrated UAS ($10.04$).
The configuration with the calibrated teacher ($9.82$) was identified through ablation.
These findings confirm that the choice of teacher policy is the dominant factor in policy-gradient performance, but they also clarify that our reported neural "best" refers specifically to this calibrated-teacher variant, which requires separate behavior-cloning initialization.
Crucially, absolute values from Protocol A and the ablation study (Protocol B) reflect different simulation horizons ($15{,}000$ vs.\ $20{,}000$ units) and are not directly comparable.

\item \textbf{Competitive comparisons limited to $\Nservers = 10$:}
The stress test (Appendix~\ref{sec:appendix_stress}) validates UAS scalability up to $\Nservers = 1{,}024$, however neither Calibrated UAS nor $\ngibbsq$ are evaluated competitively at $\Nservers > 10$.
Performing competitive assessments at larger $\Nservers$ would further substantiate the practical claims.
We scope the comparative evaluation of the empirical routing pipeline to $\Nservers = 10$. This highlights a deliberate split in our evaluation: while the $\ngibbsq$ empirical pipeline demonstrates superior optimality at small bounds, no scaling guarantee is claimed for $\ngibbsq$ or Calibrated UAS beyond the evaluated $\Nservers=10$. The analytical UAS policy, by contrast, is separately verified to scale natively to massive capacities such as $\Nservers = 1{,}024$ without the overhead of neural retraining.

\item \textbf{Coarse parameter grid for Calibrated UAS:}
The benchmark parameters $(\calbeta, \calgamma, \caloffset) = (0.85, 0.5, 0.5)$ were selected from a grid of 64 configurations evaluated on a held-out validation set.
The grid is coarse and the parameter surface may not be convex.
Therefore, a more systematic search method (e.g., Bayesian optimization) could enhance the confidence in the improvements observed.

\item \textbf{REINFORCE gradient magnitude error:}
The \reinforce{} estimator demonstrates 32.6\% relative magnitude error versus finite differences (Appendix~\ref{sec:appendix_gradient}).
While directionally validated (cosine similarity $1.0000$), the gradient signal remains somewhat noisy. The magnitude mismatch effectively reduces the learning rate, demonstrating that the full \reinforce{} training story is not fully solved and variance reduction techniques remain necessary.
Variance reduction techniques such as generalized advantage estimation (GAE) or actor-critic baselines could reduce this error; trust-region methods such as PPO would additionally stabilize step sizes.
\end{enumerate}

\subsection{Future Directions}

\begin{enumerate}[label=\textbf{F\arabic*.}, leftmargin=2.2em]
\item \textbf{Beyond the certified subclass:}
Extending the SCUAS Lyapunov argument to cover the full three-parameter family $(\calbeta, \calgamma, \caloffset)$ would close the remaining gap between the analytical and empirical layers.
The core challenge is to enlarge the theorem-backed region beyond the explicit sufficient condition $\varepsilon_{\calbeta,\calgamma,\caloffset}>0$ without sacrificing a tractable drift identity, ideally far enough to certify practically competitive calibrated points under the anchor benchmark.
The piecewise candidate in \cref{eq:piecewise_candidate} suggests that a boundary-refined Foster--Lyapunov construction based on quadratic, cubic, and imbalance terms is a concrete route for that extension.

\item \textbf{Competitive comparisons at intermediate scale:}
Competitive policy comparisons at $\Nservers \in \{32, 64, 128\}$---which connects the primary benchmark ($\Nservers = 10$) to the stress test ($\Nservers = 128{+}$)---would establish whether the learned-policy advantage persists as server count grows.

\item \textbf{Advanced RL training:}
Variance reduction via GAE or actor-critic baselines would address the \reinforce{} magnitude error identified in L5.
However, trust-region methods (PPO, natural policy gradient) could additionally improve step-size stability and accelerate convergence.

\item \textbf{Non-stationarity:}
Fluctuating arrival rates and dynamic server availability would test whether the GibbsQ stability guarantees and routing policies extend to practical non-stationary settings.
\end{enumerate}
